The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-10 Article/Article20140406Granada/LatexArt/article_main.tex
long -> duration
deleted some text and 2 \vspace{-1em}

\begin{table}[h!]
\centering
\caption{The test results of the algorithm for different configurations of learning and testing periods for a currency pair EURUSD.}
\label{tab:tab1}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning\textbackslash Test &	8	 &	10 &		15	 &	20 \\ \hline
40 &		-0.0261 &		-0.0759	 &	-0.1424	 &	-0.0653 \\ \hline
60 &		0.0044 &		-0.0156 &		0.0275 &		0.1647 \\ \hline
80 &		-0.0234 &		0.0989 &		\textbf{0.2401} &		0.0618 \\ \hline
100	 &	0.0290 &		0.0529 &		-0.0104	 &	0.0018 \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
Table \ref{tab:tab1} summarizes the results for different time periods for the first of the currency pairs. The study was conducted at approximately constant number of candles in testing period, e.g. if the testing period was 10 candles long, to perform the test on 1300 candles, optimal parameters were calculated 130 times. If the testing period was 20 candles long the parameters were changed 65 times, etc..

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys8.png}
\caption{Mileage accumulation of capital for 800 steps after 15 candles made of uses of the algorithm for the currency pair EURUSD 1h.}
\label{fig:fig8}
\end{figure}
\FloatBarrier
\vspace{-1em}
Tests were also made for another great important currency pair GBPUSD sampled every 1h. Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\

The best results are obtained in both cases (for both markets) for the learning to testing period ratio of 80/15. Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved. This result in terms of risk with Calmar ratio around 4 should be considered as engaging.\\

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
\caption{EURUSD Results per candle.}
\label{fig:fig10}
\end{figure}
\FloatBarrier
\vspace{-1em}

From these results it can be concluded that the strategy is working with a short term duration characteristics. The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
All the results presented above refer to simulations conducted in MATLAB.
%%PBStop

>>>>

\begin{table}[h!]
\centering
\caption{The test results of the algorithm for different configurations of learning and testing periods for a currency pair EURUSD.}
\label{tab:tab1}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning\textbackslash Test &	8	 &	10 &		15	 &	20 \\ \hline
40 &		-0.0261 &		-0.0759	 &	-0.1424	 &	-0.0653 \\ \hline
60 &		0.0044 &		-0.0156 &		0.0275 &		0.1647 \\ \hline
80 &		-0.0234 &		0.0989 &		\textbf{0.2401} &		0.0618 \\ \hline
100	 &	0.0290 &		0.0529 &		-0.0104	 &	0.0018 \\ \hline
\end{tabular}
\end{table}
\FloatBarrier
Table \ref{tab:tab1} summarizes the results for different time periods for the first of the currency pairs. The study was conducted at approximately constant number of candles in testing period, e.g. if the testing period was 10 candles duration, to perform the test on 1300 candles, optimal parameters were calculated 130 times. If the testing period was 20 candles long the parameters were changed 65 times, etc..

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys8.png}
\caption{Mileage accumulation of capital for 800 steps after 15 candles made of uses of the algorithm for the currency pair EURUSD 1h.}
\label{fig:fig8}
\end{figure}
\FloatBarrier
Tests were also made for another great important currency pair GBPUSD sampled every 1h. Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\

The best results are obtained in both cases (for both markets) for the learning to testing period ratio of 80/15. Result for EURUSD means that the profit higher than 100 pips per month (approximately 550 hours of trading) was achieved.\\

@@

From these results it can be concluded that the strategy is working with a short term duration characteristics. The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
All the results presented above refer to simulations conducted in MATLAB.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
\caption{EURUSD Results per candle.}
\label{fig:fig10}
\end{figure}
\FloatBarrier
%%PBStop
